---
title: "Hawaii Collection Trip Preliminary Analysis"
author: "Daniel Cook"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    toc: yes
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
require(knitr)
# devtools::install_github("wch/webshot")
library(webshot)
library(tidyverse)
opts_knit$set(progress=TRUE)

opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, print=FALSE, verbose=TRUE)
opts_chunk$set(results="asis")
opts_chunk$set(cache=TRUE,cache.path="cache/")
opts_chunk$set(fig.path="figure/",dev=c("png", "svg"))
opts_chunk$set(debug = function(before, options, envir) {
  if (!before) {
    message(
      paste(names(envir), as.list(envir),
            sep = " = ", collapse = "\n"))
  }
})


# Load Data
load("data/fulcrum/df.Rda")

# Load utility functions
source("functions.R")

```

# Overall Summary

```{r leaflet, echo = FALSE}


map_collection(df %>% dplyr::mutate(s = case_when(worms_on_sample == "Yes" ~ "green",
                                                  worms_on_sample == "Tracks" ~ "orange",
                                                  worms_on_sample == "No" ~ "grey")) , "s")


```

<h4>Worms on Sample</h4>
<div><img src='https://storage.googleapis.com/andersenlab.org/img/green.svg' width='20px'> __Yes__</div>
<div><img src='https://storage.googleapis.com/andersenlab.org/img/orange.svg' width='20px'> __Tracks__</div>
<div><img src='https://storage.googleapis.com/andersenlab.org/img/grey.svg' width='20px'> __No__</div>

## Collection over time

```{r}

library(gganimate)
library(shapefiles)

i <- ggplot(df) +  
    geom_polygon(data = shp, aes(x=X, y = Y, group = island)) +
    geom_point(aes(x=longitude, y=latitude, frame=datetime, cumulative = TRUE), color = "#ff800020") +
    theme(axis.ticks.y = element_blank(), axis.text.y = element_blank(), # get rid of x ticks/text
          axis.ticks.x = element_blank(), axis.text.x = element_blank(), # get rid of y ticks/text
          axis.title.x = element_blank(), axis.title.y = element_blank(),
          panel.background = element_blank(),
          plot.title = element_text(lineheight=.8, face="bold", vjust=1)) + 
    coord_equal(ratio=1) # square plot to avoid the distortion

gganimate::gganimate(i, interval = 0.02, filename='output.gif')

```

## Island Summary

```{r island_summary}

knitr::kable(summarize_worms_by(df, "island"))

```

## Date Summary

```{r date_summary}

knitr::kable(summarize_worms_by(df, "date"))

```

## Substrate Summary

```{r substrate_summary}

knitr::kable(summarize_worms_by(df, "substrate"))

```

## C-label Summary

```{r overall_summary}

cso %>%
  dplyr::group_by(c_label) %>%
  dplyr::mutate(n = n()) %>%
  dplyr::ungroup() %>%
  dplyr::summarize(c_label_count = length(unique(c_label)),
                   s_label_count = mean(n()),
                   s_labels_per_plate = mean(n)) %>%
  knitr::kable()

```

# Variable Summaries

## Substrate Moisture

```{r substrate_moisture}

ggplot(df) +
  geom_histogram(aes(x = substrate_moisture_)) +
  labs(x = "Substrate Moisture (%)", y = "Count") +
  facet_grid(substrate_moisture_issue~.) +
  theme_bw()

```

* On Tuesday (2017-08-08) we discovered that the moisture meter output varies depending on the mode that was set. The histogram above displays values based on those that have these issues.

## Substrate Temperature

```{r substrate_temperature}

ggplot(df) +
  geom_histogram(aes(x = substrate_temperature_c), bins=50) +
  labs(x = "Substrate Temperature (C)", y = "Count") +
  theme_bw()

```

* Substrate temperature < 9 and == 100 NA'd

## Ambient Humidty

```{r ambient_humidity}

ggplot(df) +
  geom_histogram(aes(x = ambient_humidity_), bins=50) +
  labs(x = "Ambient Humidity (%)", y = "Count") +
  theme_bw()

```

```{r ambient_temperature_c}

ggplot(df) +
  geom_histogram(aes(x = ambient_temperature_c), bins=30) +
  labs(x = "Ambient Temperature (C)", y = "Count") +
  theme_bw()

```


## Daily Collections

```{r 2017-08-02}

  
```

## Gallery

```{r gallery, results='asis', include=TRUE}
gallery(df %>% dplyr::filter(substrate == "Flower"))
```


