---
title: "Hawaii Data Guide"
author: "Daniel Cook"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    toc: yes
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
require(knitr)
# devtools::install_github("wch/webshot")
library(webshot)
library(tidyverse)
opts_knit$set(progress=TRUE)

opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, print=FALSE, verbose=TRUE)
opts_chunk$set(results="asis")
opts_chunk$set(cache=TRUE,cache.path="cache/")
opts_chunk$set(fig.path="figure/",dev=c("png", "svg"))
opts_chunk$set(debug = function(before, options, envir) {
  if (!before) {
    message(
      paste(names(envir), as.list(envir),
            sep = " = ", collapse = "\n"))
  }
})


# Load Data
load("data/fulcrum/df.Rda")

# Load utility functions
source("functions.R")

```

#  Introduction

The hawaii data is stored in `data/df.Rda`. This Rdata file contains the following:

* `df` - a dataframe of C-labels, corresponding S-labels (wide format), and associated data.
* `cso` - a long-format data frame with one row for every S-label and it's corresponding C-label.

These files are generated using `00-load.R`. __Everyone__ should review this file and understand what it is doing before using the data.

### df

`r knitr::kable(df %>% dplyr::slice(1:2) %>% dplyr::select(c_label, s_label))`

... and many more variables

### cso

`r knitr::kable(cso %>% dplyr::slice(1:2) %>% dplyr::select(c_label, s_label))`

... and many more variables

# Loading the data

When working with the Hawaii data you will want to load the data, utility functions, and a number of packages:

```{r echo = TRUE}
library(leaflet)
library(tidyverse)
library(knitr)
library(webshot)
load("data/fulcrum/df.Rda")
source("functions.R")
```

# Utility Functions

### `map_collection()`

A map can be generated of the data by using the `map_collection()` function. Please examine the function in `functions.R` and understand it before using it.

The function will filter out collections (C-labels) without a position. You can color markers accroding to a variable using a syntax like that below:

```{r leaflet, echo = TRUE}
map_collection(df %>% dplyr::mutate(color = case_when(worms_on_sample == "Yes" ~ "green",
                                                      worms_on_sample == "Tracks" ~ "orange",
                                                      worms_on_sample == "No" ~ "grey")) , "color")
```

<h4>Worms on Sample</h4>
<div><img src='https://storage.googleapis.com/andersenlab.org/img/green.svg' width='20px'> __Yes__</div>
<div><img src='https://storage.googleapis.com/andersenlab.org/img/orange.svg' width='20px'> __Tracks__</div>
<div><img src='https://storage.googleapis.com/andersenlab.org/img/grey.svg' width='20px'> __No__</div>

### `gallery()`

A gallery function is provided for convenience that will output the images from the filtered `df` object. For example:

- - - -

```{r df_out, echo = TRUE}

df %>%
  dplyr::filter(substrate == "Slug") %>%
  gallery()

```

- - - -

