---
title: "Hawaii Data Guide"
author: "Daniel Cook"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    toc: yes
    toc_float:
      collapsed: false
---

# Setup

Use the `_setup.R` script to set up the analysis environment. This will load libraries and set knitr default options.

```{r setup, include=TRUE, message=FALSE, warning=FALSE}
source("_setup.R")
```

#  Introduction

The hawaii data is stored in `data/df.Rda`. This Rdata file contains the following:

* `df` - a dataframe of C-labels, corresponding S-labels (__wide format__), and associated data.
* `cso` - a long-format data frame with one row for every S-label and it's corresponding C-label.

These files are generated using `00-load.R`. __Everyone__ should review this file and understand what it is doing before using the data.

### df

`r knitr::kable(df %>% dplyr::slice(1:2) %>% dplyr::select(c_label, s_label))`

... and many more variables

### cso

`r knitr::kable(cso %>% dplyr::slice(1:2) %>% dplyr::select(c_label, s_label))`

... and many more variables


# Utility Functions

### `map_collection()`

A map can be generated of the data by using the `map_collection()` function. Please examine the function in `functions.R` and understand it before using it.

The function will filter out collections (C-labels) without a position. You can color markers accroding to a variable using a syntax like that below:

```{r leaflet, echo = TRUE}
map_collection(df %>% dplyr::mutate(color = case_when(worms_on_sample == "Yes" ~ "green",
                                                      worms_on_sample == "Tracks" ~ "orange",
                                                      worms_on_sample == "No" ~ "grey")) , "color")


```

<h4>Worms on Sample</h4>
<div><img src='https://storage.googleapis.com/andersenlab.org/img/green.svg' width='20px'> __Yes__</div>
<div><img src='https://storage.googleapis.com/andersenlab.org/img/orange.svg' width='20px'> __Tracks__</div>
<div><img src='https://storage.googleapis.com/andersenlab.org/img/grey.svg' width='20px'> __No__</div>

### `gallery()`

A gallery function is provided for convenience that will output the images from the filtered `df` object. For example:

- - - -

```{r df_out, echo = TRUE}

df %>%
  dplyr::filter(substrate == "Slug") %>%
  gallery()

```

- - - -

